Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-10 draft.tex
separate the imperceptible features in the features section
phrasing changes

			standard size. A more detailed description of the individual features used follows:

@@

@@

		"standard" is the feature set as described above, with expanded pitch fluctuations being
		the same feature set with the addition of pitch fluctuation features with different
		comparison distances, the training batch size and the number of epochs per batch if there
		were more than one, followed by several metrics for comparison. Figures
		\ref{fig:roc_cterm}, \ref{fig:roc_mpf} and \ref{fig:roc_mpf_cterm} depict the ROC curve of
		three of the models, which were selected for use in explanation generation in the
		following section.

@@

		method, we have used selected two models from the last section and generated explanations
		on the first 500 samples of the testing data. We then summarized the explanations generated
		using both of the previously introduced metrics. A summary of the results of both metrics
		summarized by the feature is presented in tables \ref{table:exp-results-cterm},
		\ref{table:exp-results-more-pitch-flucs} and \ref{table:exp-results-mpf-cterm}. The same
		statistics are also represented graphically in the figures \ref{fig:exp_cterm},
		\ref{fig:exp_mpf} and \ref{fig:exp_mpf_cterm} respectively.

@@

		This model had similarly unpromising results, with the main difference being that all
		metrics have non-zero values, meaning that all the present features had an influence on
		the classifications which were used to generate the explanations. As with the previous
		model, HNRs and mel-spectrograms had negative overall trust values, with the addition of
		the onset strengths also presenting a negative value, implying that these features have
		caused more harm than good in the tested classifications.

>>>>

			standard size. The features we considered perceptible are as follows:

@@

			The features we consider imperceptible are described as follow:

@@

		"standard" is the feature set as described above including only one pitch-fluctuation
		feature, with expanded pitch fluctuations being the same feature set with the addition of
		more pitch fluctuation features with different comparison distances, the training batch
		size and the number of epochs per batch if there were more than one, followed by several
		metrics for comparison. Figures \ref{fig:roc_cterm}, \ref{fig:roc_mpf} and
		\ref{fig:roc_mpf_cterm} depict the ROC curve of three of the models, which were selected
		for use in explanation generation in the following section.

@@

		method, we have used selected three models from the last section and generated explanations
		on the first 500 samples of the testing data. The models selected were the best-performing
		model, without expanded pitch-fluctuation features and with three hidden layers, the
		model with expanded pitch-fluctuation features and a simple terminus, as well as the model
		with expanded pitch-fluctuation features and a terminus with three hidden layers. These
		models were selected because we wanted to firstly evaluate the best performing model, as
		well as see how the changed pitch-fluctuation feature affected the evaluation of the
		explanations. We then summarized the explanations generated using both of the previously
		introduced metrics. A summary of the results of both metrics summarized by the feature is
		presented in tables \ref{table:exp-results-cterm}, \ref{table:exp-results-more-pitch-flucs}
		and \ref{table:exp-results-mpf-cterm}. The same statistics are also represented graphically
		in the figures \ref{fig:exp_cterm}, \ref{fig:exp_mpf} and \ref{fig:exp_mpf_cterm}
		respectively.

@@

		This model had comparable results, with the main difference being that all metrics have
		non-zero values, meaning that all the present features had an influence on the
		classifications which were used to generate the explanations. As with the previous model,
		HNRs and mel-spectrograms had negative overall trust values, with the addition of the
		onset strengths also presenting a negative value, implying that these features have caused
		more harm than good in the tested classifications.
